State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2016-01-18 draft.tex
corrected Rk iteration

\newtheorem{thm}[thmcount]{Theorem}
\newtheorem{cor}[thmcount]{Corollary}

@@

To demonstrate that parametric convexity of $\mathcal W$ is necessary for convexity of $S\ominus \mathcal W(S)$, suppose that condition~(\ref{eq:def:parametrically:convex}) does not hold and choose $z_1,z_2$ so that $\mathcal W(\lambda z_1 + (1-\lambda) z_2) \not\subseteq \lambda \mathcal W(z_1) \oplus (1-\lambda) \mathcal W (z_2)$ for some $\lambda \in (0,1)$. Then there exists a value of $\lambda\in(0,1)$ such that
\begin{align*}
  \{ \lambda z_1 + (1-&\lambda)z_2
  \}\oplus \mathcal W\left( \lambda z_1 + (1-\lambda)z_2\right)\\
  % \not\subseteq&\left\{ \lambda z_1 + (1-\lambda)z_2
  % \right\}\oplus \lambda \mathcal W(z_1) \oplus (1-\lambda)
  % \mathcal W(z_2)\\
 \not\subseteq &\lambda\bigl(\{z_1\}\oplus \mathcal W(z_1)\bigr)\oplus
  (1-\lambda)\bigl(\{z_2\}\oplus \mathcal W(z_2)\bigr) .
\end{align*}
Therefore if $S$ is a convex polyhedron constructed so that $\{z_1\}\oplus\mathcal W(z_1)$ and $\{z_2\}\oplus\mathcal W(z_2)$ contain points lying on the same facet of $S$ (this is always possible if $S^\prime=S\ominus \mathcal W(S)$ has a non-empty interior), then there exists $\lambda \in (0,1)$ such that $\lambda z_1 + (1-\lambda) z_2 \notin S^\prime$.
%
%\textcolor{red}{I'm not sure this works. This only shows that it is necessary for polytopic sets, but polytopic sets are a subset of all possible sets. There might be sets for which this still works}
\end{proof}
%
Theorem~\ref{thm:convexity:of:pontryagin:difference} provides necessary and sufficient conditions for convexity of the parametric Pontryagin difference. In the next section we will show that the parametric Pontryagin difference between a polyhedral set and a piecewise affine polytopic parametric set is itself polyhedral.
%
%
%
%
%
%
\subsection{Maximal Robust Positively Invariant Sets}\label{ssec:MRPI:sets}
%
This section describes an iterative algorithm to compute the MRPI set for a linear system subject to unknown disturbances:
\[
x^+=\Psi x + v, \quad v\in\mathcal V(x),
\]
where $\mathcal V(x)$ is a continuous point-to-set map and the state $x$ is subject to the constraint $x\in\mathcal{X}$. 
%
To compute the MRPI set $\mathcal X^\infty$ we start from the constraint set $\mathcal X$ and  iteratively remove points that do not satisfy the definition~\eqref{eq:definition:MRPI:set}
by introducing constraints that exclude states for which a successor state can lie outside 
$\mathcal X$. 
%
Specifically, at each iteration $k=0,1,\ldots$, we define $\mathcal{X}_k$ as the set of initial states of the system $x^+=\Psi x + v$ such that the $i$ steps ahead state lies in $\mathcal{X}$ for all $i\in\mathbb{N}_{[0,k]}$, for all admissible disturbances. 
%
The MRPI set is then obtained as the limit of the sequence $\mathcal{X}_0,\mathcal{X}_1,\ldots$ (see e.g.~\cite{blanchini:2007}).

Let $\mathcal{X}_0=\mathcal{X}$ and for $k=1,2,\ldots$ define $\mathcal{X}_k$ as the set
\begin{equation}\label{eq:Xk:iteration}
\mathcal{X}_k = \mathcal{X}_{k-1}\cap \mathcal{D}_k 
\end{equation} 
where $\mathcal{D}_k$ contains all initial states for which the $k$ steps ahead state lies in $\mathcal{X}$. Defining $\mathcal{R}_k$, $k=0,1,\ldots$ as the sequence
\begin{equation}\label{eq:Rk:iteration}
\mathcal{R}_0 = \mathcal{X}, \quad \mathcal{R}_k = \mathcal{R}_{k-1}\ominus \Psi^{k-1} \mathcal{V}(\mathcal{R}_{k-1}),
\end{equation} 
%so that $\mathcal{R}_1 = \mathcal{X} \ominus \mathcal{V}(\mathcal{X})$, $\mathcal{R}_2 = \bigl(\mathcal{X} \ominus \mathcal{V}(\mathcal{X})\bigr) \ominus \mathcal{V}\bigl(\mathcal{X}\ominus \mathcal{V}(\mathcal{X})\bigr)$ etc., 
it follows that
\begin{equation}\label{eq:Dk:iteration}
\Psi^k \mathcal{D}_k = \mathcal{R}_k .
\end{equation}
It can therefore be shown by induction using Theorem~\ref{thm:convexity:of:pontryagin:difference} that if $\mathcal{X}$ is convex and $\mathcal{V}(x)$ is parametrically convex, then $\mathcal{R}_k$, $\mathcal{D}_k$ and $\mathcal{X}_k$ are convex for all $k$, and hence $\mathcal{X}^\infty$ is also convex.

@@

\begin{rem}\label{rem:pPdiff:calculation}
For a polyhedral set $S=\{x : h_i x \leq 1\ \forall i \in\mathcal{I} \}\subseteq \mathcal{X}$, the parametric Pontryagin difference $S \ominus \mathcal{V}(S)$ is given by
%and a para\-met\-rically convex polytopic set $\mathcal{V}(x)$, we have 
% \begin{align*}
% S \ominus \mathcal{V}(S) 
% &= \{x : h_i x + \max_{v\in \mathcal{V}(x)} h_i v \leq 1 
% \ \forall i \in\mathcal{I} \}\\
% &= \{x : h_i x + \max_{j} h_i v_j(x) \leq 1 
% \ \forall i \in\mathcal{I}\}\\
% &= \{x : h_i x + \zeta_i(x) \leq 1 
% \ \forall i \in\mathcal{I}\}, \ 
% \zeta_i(x) = \max_{j} h_i v_j(x)
% \end{align*}
\begin{align*}
S \ominus \mathcal{V}(S) 
&= \{x : h_i x + \max_{v\in \mathcal{V}(x)} h_i v \leq 1 
\ \forall i \in\mathcal{I} \}\\
&= \{x : h_i x + \underbrace{\max_{j} h_i v_j(x)}_{=\zeta_i(x)} \leq 1 
\ \forall i \in\mathcal{I}\} .
\end{align*}
Here $\zeta_i(x)$ is the solution of a mpLP and hence a continuous piecewise affine function of $x$. It follows that $S\ominus\mathcal{V}(S)$ is a convex polyhedral set.
%
To compute $\zeta_i(x)$ for all $x\in\mathcal X$ is in general a challenging problem, and a simpler method of determining the supporting hyperplanes of $S\ominus\mathcal{V}(S)$ is to include all possible affine inequalities in the set description:
\[
S\ominus\mathcal{V}(S) = \{ x : h_ix + h_i v_j(x) \leq 1, \ \forall j\in\mathbb{N}_q\ \forall i\in \mathcal I\}
\] 
and to subsequently remove redundant inequalities by applying an inequality reduction algorithm.
\end{rem}
%

Using (\ref{eq:Rk:iteration})-(\ref{eq:definition:PWA:polytopic:set:vertices}), the set $\mathcal{D}_k$ can be expressed 
\begin{subequations}\label{eq:explicit:Dk}
\begin{gather}
\mathcal{D}_k = \Bigl\{x : \xi_i \Psi^k x + \sum_{l=0}^{k-1} \zeta_{i,l}(x) \leq 1 \ \forall i \in \mathcal{I}_{\mathcal{X}}\Bigr\} \\
\zeta_{i,l}(x) = \max_{j} \xi_i \Psi^l v_j(x) ,
\end{gather}
\end{subequations}
%Clearly $\mathcal{X}_k$ is a convex polyhedral set for each finite $k$, 
and the approach described in Remark~\ref{rem:pPdiff:calculation} can be used to compute $\mathcal{X}_k = \{x: \xi_{i,k} x \leq 1,\, \forall i \in \mathcal{I}_k\}$ for each $k=0,1,\ldots$ without explicitly determining $\zeta_{i,k}(x)$ for all $x\in\mathcal{X}_{k-1}$. 
This iterative procedure is summarized as follows.
%In summary we have the following iteration.
%
\begin{alg}(Computation of MRPI set $\mathcal{X}^\infty$)\label{alg:MRPI:set}\\
\textsc{Data}: 
\begin{tabular}[t]{@{}l@{}}
$\Psi$, 
$\mathcal X= \{x: \xi_i x \leq 1 \, \forall i\in\mathcal{I}_{\mathcal{X}}\}$, 
and\\
$\mathcal{V}(x) = \conv\{\Theta_j x + \theta_j,\, j\in\mathbb{N}_q\}$.
\end{tabular}
\\
\textsc{Initialization}:
$\mathcal{X}_0 \gets \mathcal{X}$, $k\gets 1$.\\
\begin{tabular}{@{}l@{~}l@{}}
1. &
$\begin{aligned}[t]\mathcal{D}_k\gets 
\displaystyle\Bigl\{x : \xi_i \Psi^k x + \sum_{l=0}^{k-1} \xi_{i}\Psi^l(\Theta_j x &+ \theta_j)
\leq 1 \\ 
&\forall i \in \mathcal{I}_{\mathcal{X}}, \, \forall j\in\mathbb{N}_q \Bigr\};\end{aligned}$\\
2. &
\begin{tabular}[t]{@{}l@{}}
if $\mathcal{D}_k \supseteq \mathcal{X}_{k-1}$, then\\ \hspace{2em}$\mathcal{X}^\infty \gets \mathcal{X}_{k-1}$; stop;\end{tabular}\\
& 
\begin{tabular}[t]{@{}l@{}}
else\\
\hspace{2em}$\mathcal{X}_k \gets \mathcal{D}_k \cap \mathcal{X}_{k-1}$; reduce$(\mathcal{X}_k)$; $k\gets k+1$; go to 1; \end{tabular}\\
& end
% 2. &
% If $\mathcal{D}_k \supseteq \mathcal{X}_{k-1}$, then $\mathcal{X}^\infty \gets \mathcal{X}_{k-1}$; stop.\\
% & 
% Else
% $\mathcal{X}_k \gets \mathcal{D}_k \cap \mathcal{X}_{k-1}$; reduce$(\mathcal{X}_k)$; $k\gets k+1$; go to 1.
\end{tabular}
\end{alg}

%We next provide conditions under which Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
% whenever the MRPI set $\mathcal X^\infty$ is non-empty. 
%
We next show that Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations if:
%
(i) $\Psi$ is asymptotically stable, and 
%
(ii) $\Gamma$ exists such that $(\Psi,\Gamma)$ is an observable pair and $\Gamma x$ is finite whenever $x\in\mathcal{X}$.
%
%We next show that, under mild conditions, Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
%
%, so that the spectral radius, $\rho$, of $\Psi$ satisfies $\rho < 1$. We denote the pre-image of a set $S$ under the linear map $\Psi$ as $\Psi^{-1}S$; 
%
The finite determinability of the MRPI set
$\mathcal X^\infty$ implies that there exists a finite number, $M$, such 
that $\mathcal X^\infty = \mathcal X_M$, and hence  $\mathcal{X}^\infty$ is defined by a finite set of linear inequalities whenever $\mathcal X^\infty\neq \emptyset$.
%
%that $x\in\mathcal X_M$ implies $\Psi x + v \in\mathcal X_M$ for all $v\in\mathcal V(x)$, and hence $\mathcal X^\infty = \mathcal X_M$.
%
\begin{thm}\label{thm:finite:MRPI:set:state:dependable}
Let $\rho < 1$, where $\rho$ is the spectral radius of $\Psi$, and let $\mathcal{X}\subseteq\mathcal{P}$, $\mathcal{P}=\{x:\Gamma x\leq{\bf{1}}\wedge 
-\Gamma x\leq{\bf{1}}\}$, where $(\Psi,\Gamma)$ is an observable pair.
%
Then the MRPI set $\mathcal X^\infty$ for the system $x^+ = \Psi x + v$ subject to disturbances $v\in\mathcal{V}(x)$, where $\mathcal V(x)$ is a continuous point-to-set map, and constraints $x\in\mathcal{X}$, is either empty or else is a bounded polytopic set satisfying $\mathcal X^\infty =\mathcal X_M$ for finite $M$.
\end{thm}
%
%
\begin{proof}
From~\eqref{eq:Xk:iteration} and~\eqref{eq:Dk:iteration} it is clear that $\mathcal X^\infty$ is empty if $\mathcal{R}_k =\emptyset$ for some $k\geq 0$.
%
For the remainder of the proof we assume that $\mathcal{R}^\infty \neq \emptyset$ exists such that $\mathcal{R}_k \supseteq \mathcal{R}^\infty$ for all $k$.
%
The proof has two main steps: 
%
(i) we prove boundedness of $\mathcal X_k$ for all $k\geq n$, where $n$ is the state dimension;
%
(ii) we show that $\mathcal D_k$ grows exponentially with $k$, so that, for any bounded set $\mathcal C$, finite $M$ exists such that $\mathcal D_{M+1}\supseteq \mathcal{C}$. The proof is concluded by setting 
$\mathcal C = \mathcal X_{M}$ and deducing that $\mathcal X^\infty = \mathcal X_M$. 
%

For the first step, notice that $(\Psi,\Gamma)$ is observable if and only if $\mathrm{rank}(\mathcal{O}) = n$ where $\mathcal{O}^T=\begin{bmatrix} \Gamma^T \ \cdots \ 
(\Gamma\Psi^{n-1})^T\end{bmatrix}$, and this implies that the set 
%
\begin{equation}\label{eq:def:Pn}
\mathcal{P}_{n} = \{x: 
\mathcal O x\leq{\bf{1}}\wedge-\mathcal O x\leq{\bf{1}}\} = \bigcap_{k\in \mathbb N_{[0,n-1]}} \Psi^{-k} \mathcal{P}
\end{equation}
%
is bounded. 
%
(Here $\Psi^{-1}\mathcal{P}$ denotes the pre-image of $\mathcal{P}$ under the linear map $\Psi$, and $\Psi$ is not assumed to be an invertible matrix.)
%
But from (\ref{eq:Xk:iteration})-(\ref{eq:Dk:iteration}) we have $\mathcal{D}_k\subseteq \Psi^{-k}\mathcal{X} \subseteq \Psi^{-k}\mathcal{P}$ and hence $\mathcal X_k\subseteq \mathcal P_k$ for all $k$. Therefore $\mathcal X_{n}$ is bounded and $\mathcal{X}^\infty$ is also bounded since $\mathcal{X}_k\supseteq\mathcal{X}_{k+1}\supseteq\mathcal{X}^\infty$ for all $k$.

To see that $\mathcal{D}_k$ grows exponentially, let $r_1$ be the radius of the largest ball centred on the origin that is contained in $\mathcal{R}^\infty$ so that $\mathcal{R}^\infty \supseteq r_1\mathcal{E}$ (where 
for notational convenience we write $\mathcal E=B_1(0)$). Then (\ref{eq:Dk:iteration}) implies $\mathcal{D}_k=\Psi^{-k}\mathcal{R}_k\supseteq\rho^{-k}r_1\mathcal{E}$.

>>>>

\newtheorem{thm}[thmcount]{Theorem}
\newtheorem{cor}[thmcount]{Corollary}
\newtheorem{prop}[thmcount]{Proposition}

@@

To demonstrate that parametric convexity of $\mathcal W$ is necessary for convexity of $S\ominus \mathcal W(S)$, suppose that condition~(\ref{eq:def:parametrically:convex}) does not hold and choose $z_1,z_2$ so that $\mathcal W(\lambda z_1 + (1-\lambda) z_2) \not\subseteq \lambda \mathcal W(z_1) \oplus (1-\lambda) \mathcal W (z_2)$ for some $\lambda \in (0,1)$. Then there exists a value of $\lambda\in(0,1)$ such that
\begin{align*}
  \{ \lambda z_1 + (1-&\lambda)z_2
  \}\oplus \mathcal W\left( \lambda z_1 + (1-\lambda)z_2\right)\\
  % \not\subseteq&\left\{ \lambda z_1 + (1-\lambda)z_2
  % \right\}\oplus \lambda \mathcal W(z_1) \oplus (1-\lambda)
  % \mathcal W(z_2)\\
 \not\subseteq &\lambda\bigl(\{z_1\}\oplus \mathcal W(z_1)\bigr)\oplus
  (1-\lambda)\bigl(\{z_2\}\oplus \mathcal W(z_2)\bigr) .
\end{align*}
Therefore if $S$ is a convex polyhedron constructed so that $\{z_1\}\oplus\mathcal W(z_1)$ and $\{z_2\}\oplus\mathcal W(z_2)$ contain points lying on the same facet of $S$ (this is always possible if $S^\prime=S\ominus \mathcal W(S)$ has a non-empty interior), then there exists $\lambda \in (0,1)$ such that $\lambda z_1 + (1-\lambda) z_2 \notin S^\prime$.
%
\end{proof}
%
Theorem~\ref{thm:convexity:of:pontryagin:difference} provides necessary and sufficient conditions for convexity of the parametric Pontryagin difference. In the next section we will show that the parametric Pontryagin difference between a polyhedral set and a piecewise affine polytopic parametric set is itself polyhedral.
%
%
%
%
%
%
\subsection{Maximal Robust Positively Invariant Sets}\label{ssec:MRPI:sets}
%
This section describes an iterative algorithm to compute the MRPI set for a linear system subject to unknown disturbances:
\[
x^+=\Psi x + v, \quad v\in\mathcal V(x),
\]
where $\mathcal V(x)$ is a continuous point-to-set map and the state $x$ is subject to the constraint $x\in\mathcal{X}$. 
%
To compute the MRPI set $\mathcal X^\infty$ we start from the constraint set $\mathcal X$ and  iteratively remove points that do not satisfy the definition~\eqref{eq:definition:MRPI:set}
by introducing constraints that exclude states for which a successor state can lie outside 
$\mathcal X$. 
%
Specifically, at each iteration $k=0,1,\ldots$, we define $\mathcal{X}_k$ as the set of initial states of the system $x^+=\Psi x + v$ such that the $i$ steps ahead state lies in $\mathcal{X}$ for all $i\in\mathbb{N}_{[0,k]}$, for all admissible disturbances. 
%
The MRPI set is then obtained as the limit of the sequence $\mathcal{X}_0,\mathcal{X}_1,\ldots$ (see e.g.~\cite{blanchini:2007}).

\textcolor{red}{%
Let $\mathcal{X}_0=\mathcal{X}$ and for $k=1,2,\ldots$ define $\mathcal{X}_k$ as the set
\begin{equation}\label{eq:Xk:iteration}
\mathcal{X}_k = \mathcal{X}_{k-1}\cap \mathcal{D}_k 
\end{equation} 
where $\mathcal{D}_k$ is the set of initial states for which the $k$ steps ahead state lies in $\mathcal{X}$ for all admissible disturbances.
%
To explain how $\mathcal{X}_k$ is computed and to simplify the analysis of $\mathcal{X}^\infty$, we define $\mathcal{R}_0,\mathcal{R}_1,\ldots$ as the sequence with $\mathcal{R}_0 = \mathcal{X}$ and
\begin{equation}\label{eq:Rk:iteration}
\mathcal{R}_k = \mathcal{R}_{k-1}\ominus \Psi^{k-1} \mathcal{V}_k(\mathcal{R}_{k-1}) \ \forall k=1,2\ldots,
\end{equation} 
with $\mathcal{V}_k$ defined as the point-to-set map $\mathcal{V}_k(x) = \mathcal{V}(\Psi^{-k} x)$.%
}

\textcolor{red}{%
\begin{prop}\label{prop:Dk:iteration}
$\mathcal{D}_k = \Psi^{-k}\mathcal{R}_k$ for all $k\geq 0$.
\end{prop}%
}

\textcolor{red}{%
\begin{proof}
Since $\mathcal{D}_k$ is the set of initial states for which the state $k$ steps ahead lies in $\mathcal{X}$, we have $\mathcal{D}_0 = \mathcal{X}$ and
%, for $k\geq 1$,
\[
\mathcal{D}_k = \bigl\{ x : \{\Psi x\} \oplus \mathcal{V}(x) \subseteq \mathcal{D}_{k-1}\bigr\}  
\ \forall k = 1,2\ldots 
\]
Hence for $k\geq 1$, $\Psi^k \mathcal{D}_k$ is given by
\begin{align*}
\Psi^k\mathcal{D}_k &= \bigl\{ \Psi^k x : \{\Psi x\} \oplus \mathcal{V}(x) \subseteq \mathcal{D}_{k-1}\bigr\} \\
& = \bigl\{ y : \{\Psi^{-k+1} y\} \oplus \mathcal{V}_k(y) \subseteq \mathcal{D}_{k-1}\bigr\} \\
& = \bigl\{ y : \{ y\} \oplus \Psi^{k-1}\mathcal{V}_k(y) \subseteq \Psi^{k-1}\mathcal{D}_{k-1}\bigr\} .
\end{align*}
Using the definition of the parametric Pontryagin difference, this implies
\[
\Psi^{k}\mathcal{D}_k = (\Psi^{k-1}\mathcal{D}_{k-1}) \ominus \Psi^{k-1}\mathcal{V}_k(\Psi^{k-1}\mathcal{D}_{k-1}) \ \forall k=1,2\ldots 
\]
and the result therefore follows from  $\mathcal{R}_0=\mathcal{D}_0$ and (\ref{eq:Rk:iteration}).
%
% so if $\Psi^{k}\mathcal{D}_k = \mathcal{R}_k$ and $\Psi^{k-1}\mathcal{D}_{k-1} = \mathcal{R}_{k-1}$, then by the definition of the parametric Pontryagin difference we have
% \[
% \mathcal{R}_k = \mathcal{R}_{k-1}\ominus \Psi^{k-1} \mathcal{V}_k(\mathcal{R}_{k-1}), \ \forall k=1,2,\ldots,
% \]
% and the result follows from
% (\ref{eq:Rk:iteration}) and $\mathcal{R}_0=\mathcal{D}_0 = \mathcal{X}$.
\end{proof}%
}

\textcolor{red}{%
\begin{rem}
It can be shown by induction using (\ref{eq:Rk:iteration}) and Theorem~\ref{thm:convexity:of:pontryagin:difference} that if $\mathcal{X}$ is convex and $\mathcal{V}(x)$ is parametrically convex, then $\mathcal{R}_k$, $\mathcal{D}_k$ and $\mathcal{X}_k$ are convex for all $k$, and hence $\mathcal{X}^\infty$ is also convex.
\end{rem}%
}

% Let $\mathcal{X}_0=\mathcal{X}$ and for $k=1,2,\ldots$ define $\mathcal{X}_k$ as the set
% \begin{equation}\label{eq:Xk:iteration}
% \mathcal{X}_k = \mathcal{X}_{k-1}\cap \mathcal{D}_k 
% \end{equation} 
% where $\mathcal{D}_k$ contains all initial states for which the $k$ steps ahead state lies in $\mathcal{X}$. Defining $\mathcal{R}_k$, $k=0,1,\ldots$ as the sequence
% \begin{equation}\label{eq:Rk:iteration}
% \mathcal{R}_0 = \mathcal{X}, \quad \mathcal{R}_k = \mathcal{R}_{k-1}\ominus \Psi^{k-1} \mathcal{V}(\mathcal{R}_{k-1}),
% \end{equation} 
% %so that $\mathcal{R}_1 = \mathcal{X} \ominus \mathcal{V}(\mathcal{X})$, $\mathcal{R}_2 = \bigl(\mathcal{X} \ominus \mathcal{V}(\mathcal{X})\bigr) \ominus \mathcal{V}\bigl(\mathcal{X}\ominus \mathcal{V}(\mathcal{X})\bigr)$ etc., 
% it follows that
% \begin{equation}\label{eq:Dk:iteration}
% \Psi^k \mathcal{D}_k = \mathcal{R}_k .
% \end{equation}
% It can therefore be shown by induction using Theorem~\ref{thm:convexity:of:pontryagin:difference} that if $\mathcal{X}$ is convex and $\mathcal{V}(x)$ is parametrically convex, then $\mathcal{R}_k$, $\mathcal{D}_k$ and $\mathcal{X}_k$ are convex for all $k$, and hence $\mathcal{X}^\infty$ is also convex.

@@

\begin{rem}\label{rem:pPdiff:calculation}
For a convex polyhedron $S=\{x : h_i x \leq 1$ $\forall i \in\mathcal{I} \}$ the parametric Pontryagin difference $S \ominus \mathcal{V}(S)$ is given by
%
%The parametric Pontryagin difference $S \ominus \mathcal{V}(S)$, for a convex polyhedral set $S=\{x : h_i x \leq 1\ \forall i \in\mathcal{I} \}$, is given by
%
%and a para\-met\-rically convex polytopic set $\mathcal{V}(x)$, we have 
% \begin{align*}
% S \ominus \mathcal{V}(S) 
% &= \{x : h_i x + \max_{v\in \mathcal{V}(x)} h_i v \leq 1 
% \ \forall i \in\mathcal{I} \}\\
% &= \{x : h_i x + \max_{j} h_i v_j(x) \leq 1 
% \ \forall i \in\mathcal{I}\}\\
% &= \{x : h_i x + \zeta_i(x) \leq 1 
% \ \forall i \in\mathcal{I}\}, \ 
% \zeta_i(x) = \max_{j} h_i v_j(x)
% \end{align*}
\begin{align*}
S \ominus \mathcal{V}(S) 
&= \{x : h_i x + \max_{v\in \mathcal{V}(x)} h_i v \leq 1 
\ \forall i \in\mathcal{I} \}\\
&= \{x : h_i x + \underbrace{\max_{j} h_i v_j(x)}_{=\zeta_i(x)} \leq 1 
\ \forall i \in\mathcal{I}\} .
\end{align*}
Here $\zeta_i(x)$ is the solution of a mpLP and hence is a continuous piecewise affine function of $x$~\cite{Gal:1995}. It follows that $S\ominus\mathcal{V}(S)$ is a convex polyhedral set.
%
To compute $\zeta_i(x)$ for all $x\in\mathcal X$ is in general a challenging problem, and a simpler method of determining the supporting hyperplanes of $S\ominus\mathcal{V}(S)$ is to include all possible affine inequalities in the set description:
\[
S\ominus\mathcal{V}(S) = \{ x : h_ix + h_i v_j(x) \leq 1, \ \forall j\in\mathbb{N}_q\ \forall i\in \mathcal I\}
\] 
and to subsequently remove redundant inequalities by applying an inequality reduction algorithm. 
\textcolor{red}{%
The resulting set can be expressed $S\ominus \mathcal{V}(S) = \{ x : h_i^\prime x \leq 1 \ \forall i \in \mathcal{I}^\prime \}$.%
}%
\end{rem}
%

\textcolor{red}{Given $\mathcal{R}_{k-1} = \{ x : \xi_{i,k-1} x \leq 1 \ \forall i \in \mathcal{I}_{k-1}\}$, we can compute $\mathcal{R}_k$ using (\ref{eq:Rk:iteration}) and (\ref{eq:definition:PWA:polytopic:set:vertices}) as
\begin{subequations}\label{eq:Rk:explicit}
\begin{gather}
\mathcal{R}_k = \Bigl\{ x : \xi_{i,k-1} x + \zeta_{i,k-1}(x) \leq 1 \ \forall i \in \mathcal{I}_{k-1} \Bigr\} \\
\zeta_{i,k-1}(x) = \max_{j} \xi_{i,k-1} \Psi^{k-1} v_j(\Psi^{-k}x) ,
\end{gather}
\end{subequations}
and the approach outlined in Remark~\ref{rem:pPdiff:calculation} can be used to compute $\mathcal{R}_k = \{x: \xi_{i,k} x \leq 1\, \forall i \in \mathcal{I}_k\}$ without explicitly determining $\zeta_{i,k-1}(x)$ for all $x\in\mathcal{R}_{k-1}$. This gives $\mathcal{X}_k = \mathcal{X}_{k-1}\cap \{x: \xi_{i,k}\Psi^k x \leq 1\, \forall i \in \mathcal{I}_k\}$,%
}
%
% Using (\ref{eq:Rk:iteration})-(\ref{eq:definition:PWA:polytopic:set:vertices}), the set $\mathcal{D}_k$ can be expressed 
% \begin{subequations}\label{eq:explicit:Dk}
% \begin{gather}
% \mathcal{D}_k = \Bigl\{x : \xi_i \Psi^k x + \sum_{l=0}^{k-1} \zeta_{i,l}(x) \leq 1 \ \forall i \in \mathcal{I}_{\mathcal{X}}\Bigr\} \\
% \zeta_{i,l}(x) = \max_{j} \xi_i \Psi^l v_j(x) ,
% \end{gather}
% \end{subequations}
% %Clearly $\mathcal{X}_k$ is a convex polyhedral set for each finite $k$, 
% and the approach described in Remark~\ref{rem:pPdiff:calculation} can be used to compute $\mathcal{X}_k = \{x: \xi_{i,k} x \leq 1,\, \forall i \in \mathcal{I}_k\}$ for each $k=0,1,\ldots$ without explicitly determining $\zeta_{i,k}(x)$ for all $x\in\mathcal{X}_{k-1}$. 
%
and the implied iteration is summarized as follows.
%
\begin{alg}(Computation of MRPI set $\mathcal{X}^\infty$)\label{alg:MRPI:set}\\
\textsc{Data}: 
\begin{tabular}[t]{@{}l@{}}
$\Psi$, 
$\mathcal X= \{x: \xi_i x \leq 1 \, \forall i\in\mathcal{I}_{\mathcal{X}}\}$, 
and\\
$\mathcal{V}(x) = \conv\{\Theta_j x + \theta_j,\, j\in\mathbb{N}_q\}$.
\end{tabular}
\\
\textsc{Initialization}:
$\mathcal{X}_0 \gets \mathcal{X}$, \textcolor{red}{$\mathcal{R}_0 \gets \mathcal{X}$}, $k\gets 1$.\\
% \begin{tabular}[t]{@{}l@{}}
% $\mathcal{X}_0 \gets \mathcal{X}$, 
% \textcolor{red}{$\mathcal{I}_0\gets \mathcal{I}_{\mathcal{X}}$, 
% $\xi_{i,0}\gets \xi_i\, \forall i\in\mathcal{I}_0$}\\
% \textcolor{red}{$k\gets 1$.}\end{tabular}\\
\begin{tabular}{@{}l@{~}l@{}}
1. &
\textcolor{red}{%
Compute $\mathcal{R}_k = \{x: \xi_{i,k} x \leq 1\, \forall i \in \mathcal{I}_k\}$ using (\ref{eq:Rk:explicit}a,b)%
}\\ 
& 
\textcolor{red}{%
and 
$\mathcal{D}_k \gets \Psi^{-k}\mathcal{R}_k$.%
}\\
% $\begin{aligned}[t]\mathcal{D}_k\gets 
% \displaystyle\Bigl\{x : \xi_i \Psi^k x + \sum_{l=0}^{k-1} \xi_{i}\Psi^l(\Theta_j x &+ \theta_j)
% \leq 1 \\ 
% &\forall i \in \mathcal{I}_{\mathcal{X}}, \, \forall j\in\mathbb{N}_q \Bigr\};\end{aligned}$\\
2. &
\begin{tabular}[t]{@{}l@{}}
If $\mathcal{D}_k \supseteq \mathcal{X}_{k-1}$, then\\ \hspace{2em}$\mathcal{X}^\infty \gets \mathcal{X}_{k-1}$; stop;\end{tabular}\\
& 
\begin{tabular}[t]{@{}l@{}}
else\\
\hspace{2em}$\mathcal{X}_k \gets \mathcal{D}_k \cap \mathcal{X}_{k-1}$; reduce$(\mathcal{X}_k)$; $k\gets k+1$; go to 1; \end{tabular}\\
& end
% 2. &
% If $\mathcal{D}_k \supseteq \mathcal{X}_{k-1}$, then $\mathcal{X}^\infty \gets \mathcal{X}_{k-1}$; stop.\\
% & 
% Else
% $\mathcal{X}_k \gets \mathcal{D}_k \cap \mathcal{X}_{k-1}$; reduce$(\mathcal{X}_k)$; $k\gets k+1$; go to 1.
\end{tabular}
\end{alg}

%We next provide conditions under which Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
% whenever the MRPI set $\mathcal X^\infty$ is non-empty. 
%
We next show that Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations if:
%
(i) $\Psi$ is asymptotically stable, and 
%
(ii) $\Gamma$ exists such that $(\Psi,\Gamma)$ is an observable pair and $\Gamma x$ is finite whenever $x\in\mathcal{X}$.
%
%We next show that, under mild conditions, Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
%
%, so that the spectral radius, $\rho$, of $\Psi$ satisfies $\rho < 1$. We denote the pre-image of a set $S$ under the linear map $\Psi$ as $\Psi^{-1}S$; 
%
The finite determinability of the MRPI set
$\mathcal X^\infty$ implies that there exists a finite number, $M$, such 
that $\mathcal X^\infty = \mathcal X_M$, and hence  $\mathcal{X}^\infty$ is defined by a finite set of linear inequalities whenever $\mathcal X^\infty\neq \emptyset$.
%
%that $x\in\mathcal X_M$ implies $\Psi x + v \in\mathcal X_M$ for all $v\in\mathcal V(x)$, and hence $\mathcal X^\infty = \mathcal X_M$.
%
\begin{thm}\label{thm:finite:MRPI:set:state:dependable}
Let $\rho < 1$, where $\rho$ is the spectral radius of $\Psi$, and let $\mathcal{X}\subseteq\mathcal{P}$, $\mathcal{P}=\{x:\Gamma x\leq{\bf{1}}\wedge 
-\Gamma x\leq{\bf{1}}\}$, where $(\Psi,\Gamma)$ is an observable pair.
%
Then the MRPI set $\mathcal X^\infty$ for the system $x^+ = \Psi x + v$ subject to disturbances $v\in\mathcal{V}(x)$, where $\mathcal V(x)$ is a continuous point-to-set map, and constraints $x\in\mathcal{X}$, is either empty or else is a bounded polytopic set satisfying $\mathcal X^\infty =\mathcal X_M$ for finite $M$.
\end{thm}
%
%
\begin{proof}
From~\eqref{eq:Xk:iteration} and Proposition~\ref{prop:Dk:iteration} it is clear that $\mathcal X^\infty$ is empty if $\mathcal{R}_k =\emptyset$ for some $k\geq 0$.
%
For the remainder of the proof we assume that $\mathcal{R}^\infty \neq \emptyset$ exists such that $\mathcal{R}_k \supseteq \mathcal{R}^\infty$ for all $k$.
%
The proof has two main steps: 
%
(i) we prove boundedness of $\mathcal X_k$ for all $k\geq n$, where $n$ is the state dimension;
%
(ii) we show that $\mathcal D_k$ grows exponentially with $k$, so that, for any bounded set $\mathcal C$, finite $M$ exists such that $\mathcal D_{M+1}\supseteq \mathcal{C}$. The proof is concluded by setting 
$\mathcal C = \mathcal X_{M}$ and deducing that $\mathcal X^\infty = \mathcal X_M$. 
%
